### 2020-11-27 README.Rmd
makefile in README files

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

@@

>>>>

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations

@@

Makefile:
Whatever the option you choose to explore this compendium, you can also use the makefile (`/analysis/makefile`) in the terminal (`make all`) to compile the .docx document and then, you can use `make clean` to remove all files generated during the process.
